They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-12 paper.tex
Paper: add genetic alg section

In \tavs,

>>>>

In \tavs, evolution is done in three steps: culling, reproduction, and mutation.
To cull the genomes with low fitness, the entire range of genome values is
compressed down on to the values from zero to one, and then fed through a square
root function. The result is the probability that the given genome survives to
the next wave. The square root function has the nice properties that it passes
through \((1,1)\), so at least one genome will always survive, it passes through
\((0,0)\), so at least one genome will die, and other values are scaled
non-linearly such that only the really unfit genomes have a high probability of
dying.

The surviving genomes are then passed to the reproduction function, which
selects a weighted random genome to duplicate and add to the next wave until
the total is back up to the set population count. The randomness is weighted
linearly; all of the genome fitnesses are summed, and then a random number is
picked between 0 and this sum, effectively creating a ``bucket'' the size of the
each fitness for the random number to choose between.

The mutation phase takes the result of reproduction and adds a
Gaussian-distributed random value to each characteristic of the Genome. The
results are then passed to the game portion to be spawned as another wave of
Zombunnies.
